**Dynamics of Epiphytic Microbial Communities on Marine Macrophyte Surfaces**

### 2020-02-04 submission/manuscript.Rmd
Logfile remove logic.

\newpage
## Figures
\newpage
```{r out.width="100%", fig.align="center", fig.cap="Taxonomic classification and relative contribution of the most abundant bacterial sequences.\\label{community}", fig.pos="ht"}
include_graphics("../results/figures/community_bar_plot.jpg")
```

>>>>

\newpage
## Figures
\newpage
```{r out.width="80%", fig.align="center", fig.cap="Taxonomic classification and relative contribution of the most abundant bacterial sequences.\\label{community}", fig.pos="ht"}
include_graphics("../results/figures/community_bar_plot.jpg")
```
